Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-10-10 STAT-paper-template/APA/fertile.tex
hard-coded latex file

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... -------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ---------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Error in eval\_tidy(xs[[j]], mask): object '.Random.seed' not found}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks -------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ---------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval\_tidy(xs[[j]], mask): object '.Random.seed' not found}}\end{kframe}
\end{knitrout}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ---------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval\_tidy(xs[[j]], mask): object '.Random.seed' not found}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-10 00:39:23
## 2 package:for~ <NA>                                 base::l~ 2020-10-10 00:39:23
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-10 00:39:23
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "readr::read_csv")
##     check_path_safe(file, ... = "readr::read_csv")
##     readr::read_csv(file, ...)
##   }
## }
## <bytecode: 0x7fcede54ad08>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpNAq0UZ/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpNAq0UZ/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpNAq0UZ/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpNAq0UZ/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
\bibliography{refs}%

>>>>

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... ---------------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ------------------------------------ fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks ---------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Checking for no absolute paths}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Checking for only portable paths}}\end{kframe}
\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Summary of fertile checks --------------------------------- fertile 0.0.0.9027 --}}\end{kframe}
\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Reproducibility checks passed: 2}}\end{kframe}
\end{knitrout}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Analysis of reproducibility for project\_miceps ------------ fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Packages referenced in source code ---------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## # A tibble: 9 x 3
##   package       N used_in                    
##   <chr>     <int> <chr>                      
## 1 broom         1 project_miceps/analysis.Rmd
## 2 dplyr         1 project_miceps/analysis.Rmd
## 3 ggplot2       1 project_miceps/analysis.Rmd
## 4 purrr         1 project_miceps/analysis.Rmd
## 5 readr         1 project_miceps/analysis.Rmd
## 6 rmarkdown     1 project_miceps/analysis.Rmd
## 7 skimr         1 project_miceps/analysis.Rmd
## 8 stargazer     1 project_miceps/analysis.Rmd
## 9 tidyr         1 project_miceps/analysis.Rmd
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Files present in directory ------------------------------ fertile 0.0.0.9027 --}}\begin{verbatim}
##                      file   ext    size
## 1 Estrogen_Receptors.docx  docx  10.97K
## 2      citrate_v_time.png   png 188.08K
## 3     proteins_v_time.png   png 378.45K
## 4   Blot_data_updated.csv   csv  14.43K
## 5      CS_data_redone.csv   csv   7.39K
## 6                mice.csv   csv  14.33K
## 7               README.md    md      39
## 8            miceps.Rproj Rproj     204
## 9            analysis.Rmd   Rmd   4.94K
##                                                                      mime
## 1 application/vnd.openxmlformats-officedocument.wordprocessingml.document
## 2                                                               image/png
## 3                                                               image/png
## 4                                                                text/csv
## 5                                                                text/csv
## 6                                                                text/csv
## 7                                                           text/markdown
## 8                                                            text/rstudio
## 9                                                         text/x-markdown
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Suggestions for moving files ---------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
##                  path_rel    dir_rel
## 1   Blot_data_updated.csv   data-raw
## 2      CS_data_redone.csv   data-raw
## 3 Estrogen_Receptors.docx inst/other
## 4            analysis.Rmd  vignettes
## 5      citrate_v_time.png inst/image
## 6                mice.csv   data-raw
## 7     proteins_v_time.png inst/image
##                                                                                                cmd
## 1     file_move('project_miceps/Blot_data_updated.csv', fs::dir_create('project_miceps/data-raw'))
## 2        file_move('project_miceps/CS_data_redone.csv', fs::dir_create('project_miceps/data-raw'))
## 3 file_move('project_miceps/Estrogen_Receptors.docx', fs::dir_create('project_miceps/inst/other'))
## 4             file_move('project_miceps/analysis.Rmd', fs::dir_create('project_miceps/vignettes'))
## 5      file_move('project_miceps/citrate_v_time.png', fs::dir_create('project_miceps/inst/image'))
## 6                  file_move('project_miceps/mice.csv', fs::dir_create('project_miceps/data-raw'))
## 7     file_move('project_miceps/proteins_v_time.png', fs::dir_create('project_miceps/inst/image'))
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Problematic paths logged -------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-10 13:33:50
## 2 package:for~ <NA>                                 base::l~ 2020-10-10 13:33:50
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-10 13:33:50
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "readr::read_csv")
##     check_path_safe(file, ... = "readr::read_csv")
##     readr::read_csv(file, ...)
##   }
## }
## <bytecode: 0x7fea6a6f2048>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpxR3hjP/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpxR3hjP/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpxR3hjP/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpxR3hjP/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
%\bibliography{refs}%

\begin{thebibliography}{}

\bibitem [\protect \citeauthoryear {%
Baker%
}{%
Baker%
}{%
{\protect \APACyear {2016}}%
}]{%
baker20161}
\APACinsertmetastar {%
baker20161}%
\begin{APACrefauthors}%
Baker, M.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2016}{}{}.
\newblock
{\BBOQ}\APACrefatitle {1,500 scientists lift the lid on reproducibility} {1,500
  scientists lift the lid on reproducibility}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Nature News}{533}{7604}{452}.
\newblock
\begin{APACrefURL}
  \url{https://www.nature.com/news/1-500-scientists-lift-the-lid-on-reproducibility-1.19970}
  \end{APACrefURL}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Baumer%
\ \BBA {} Bertin%
}{%
Baumer%
\ \BBA {} Bertin%
}{%
{\protect \APACyear {2020}}%
}]{%
R-fertile}
\APACinsertmetastar {%
R-fertile}%
\begin{APACrefauthors}%
Baumer, B\BPBI S.%
\BCBT {}\ \BBA {} Bertin, A\BPBI M.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2020}{}{}.
\newblock
\APACrefbtitle {fertile: creating optimal conditions for reproducibility.}
  {fertile: creating optimal conditions for reproducibility.}
\newblock
\begin{APACrefURL} \url{https://github.com/baumer-lab/fertile} \end{APACrefURL}
\newblock
\APACrefnote{R package version 0.0.0.9027}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
J.~Blischak%
, Carbonetto%
\BCBL {}\ \BBA {} Stephens%
}{%
J.~Blischak%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2019}}%
}]{%
R-workflowr}
\APACinsertmetastar {%
R-workflowr}%
\begin{APACrefauthors}%
Blischak, J.%
, Carbonetto, P.%
\BCBL {}\ \BBA {} Stephens, M.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2019}{}{}.
\newblock
\APACrefbtitle {workflowr: A Framework for Reproducible and Collaborative Data
  Science.} {workflowr: A framework for reproducible and collaborative data
  science.}
\newblock
\begin{APACrefURL} \url{https://CRAN.R-project.org/package=workflowr}
  \end{APACrefURL}
\newblock
\APACrefnote{R package version 1.6.0}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
J\BPBI D.~Blischak%
, Carbonetto%
\BCBL {}\ \BBA {} Stephens%
}{%
J\BPBI D.~Blischak%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2019}}%
}]{%
workflowr2019}
\APACinsertmetastar {%
workflowr2019}%
\begin{APACrefauthors}%
Blischak, J\BPBI D.%
, Carbonetto, P.%
\BCBL {}\ \BBA {} Stephens, M.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2019}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Creating and sharing reproducible research code the
  workflowr way} {Creating and sharing reproducible research code the workflowr
  way}.{\BBCQ}
\newblock
\APACjournalVolNumPages{F1000Research}{8}{1749}{}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.12688/f1000research.20843.1}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} 10.12688/f1000research.20843.1 \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Broman%
}{%
Broman%
}{%
{\protect \APACyear {2019}}%
}]{%
broman}
\APACinsertmetastar {%
broman}%
\begin{APACrefauthors}%
Broman, K.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2019}{}{}.
\newblock
\APACrefbtitle {initial steps toward reproducible research: organize your data
  and code.} {initial steps toward reproducible research: organize your data
  and code.}
\newblock
\begin{APACrefURL} \url{https://kbroman.org/steps2rr/pages/organize.html}
  \end{APACrefURL}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Cooper%
\ \protect \BOthers {.}}{%
Cooper%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2017}}%
}]{%
cooper2017guide}
\APACinsertmetastar {%
cooper2017guide}%
\begin{APACrefauthors}%
Cooper, N.%
, Hsing, P\BHBI Y.%
, Croucher, M.%
, Graham, L.%
, James, T.%
, Krystalli, A.%
\BCBL {}\ \BBA {} Michonneau, F.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2017}{}{}.
\newblock
\APACrefbtitle {A guide to reproducible code in ecology and evolution.} {A
  guide to reproducible code in ecology and evolution.}
\newblock
\begin{APACrefURL}
  \url{https://www.britishecologicalsociety.org/wp-content/uploads/2017/12/guide-to-reproducible-code.pdf}
  \end{APACrefURL}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Eisner%
}{%
Eisner%
}{%
{\protect \APACyear {2018}}%
}]{%
eisner-reproducibility}
\APACinsertmetastar {%
eisner-reproducibility}%
\begin{APACrefauthors}%
Eisner, D\BPBI A.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2018}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Reproducibility of science: Fraud, impact factors and
  carelessness} {Reproducibility of science: Fraud, impact factors and
  carelessness}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Journal of Molecular and Cellular
  Cardiology}{114}{}{364-368}.
\newblock
\begin{APACrefURL}
  \url{http://www.sciencedirect.com/science/article/pii/S0022282817303334}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} https://doi.org/10.1016/j.yjmcc.2017.10.009 \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Fidler%
\ \BBA {} Wilcox%
}{%
Fidler%
\ \BBA {} Wilcox%
}{%
{\protect \APACyear {2018}}%
}]{%
sep-scientific-reproducibility}
\APACinsertmetastar {%
sep-scientific-reproducibility}%
\begin{APACrefauthors}%
Fidler, F.%
\BCBT {}\ \BBA {} Wilcox, J.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2018}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Reproducibility of Scientific Results} {Reproducibility
  of scientific results}.{\BBCQ}
\newblock
\BIn{} E\BPBI N.~Zalta\ (\BED), \APACrefbtitle {The Stanford Encyclopedia of
  Philosophy} {The stanford encyclopedia of philosophy}\ (\PrintOrdinal{Winter
  2018}\ \BEd).
\newblock
\APACaddressPublisher{}{Metaphysics Research Lab, Stanford University}.
\newblock
\APAChowpublished
  {\url{https://plato.stanford.edu/archives/win2018/entries/scientific-reproducibility/}}.
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
FitzJohn%
\ \protect \BOthers {.}}{%
FitzJohn%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2020}}%
}]{%
R-orderly}
\APACinsertmetastar {%
R-orderly}%
\begin{APACrefauthors}%
FitzJohn, R.%
, Ashton, R.%
, Hill, A.%
, Eden, M.%
, Hinsley, W.%
, Russell, E.%
\BCBL {}\ \BBA {} Thompson, J.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2020}{}{}.
\newblock
\APACrefbtitle {orderly: Lightweight Reproducible Reporting.} {orderly:
  Lightweight reproducible reporting.}
\newblock
\begin{APACrefURL} \url{https://CRAN.R-project.org/package=orderly}
  \end{APACrefURL}
\newblock
\APACrefnote{R package version 1.0.4}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Gancarz%
}{%
Gancarz%
}{%
{\protect \APACyear {2003}}%
}]{%
unix}
\APACinsertmetastar {%
unix}%
\begin{APACrefauthors}%
Gancarz, M.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYear{2003}.
\newblock
\APACrefbtitle {Linux and the Unix Philosophy} {Linux and the unix philosophy}\
  (\PrintOrdinal{2nd}\ \BEd).
\newblock
\APACaddressPublisher{Woburn, MA}{Digital Press}.
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Goodman%
, Fanelli%
\BCBL {}\ \BBA {} Ioannidis%
}{%
Goodman%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2016}}%
}]{%
Goodman341ps12}
\APACinsertmetastar {%
Goodman341ps12}%
\begin{APACrefauthors}%
Goodman, S\BPBI N.%
, Fanelli, D.%
\BCBL {}\ \BBA {} Ioannidis, J\BPBI P\BPBI A.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2016}{}{}.
\newblock
{\BBOQ}\APACrefatitle {What does research reproducibility mean?} {What does
  research reproducibility mean?}{\BBCQ}
\newblock
\APACjournalVolNumPages{Science Translational Medicine}{8}{341}{1--6}.
\newblock
\begin{APACrefURL} \url{https://stm.sciencemag.org/content/8/341/341ps12}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} 10.1126/scitranslmed.aaf5027 \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Gosselin%
}{%
Gosselin%
}{%
{\protect \APACyear {2020}}%
}]{%
bioessays-gosselin}
\APACinsertmetastar {%
bioessays-gosselin}%
\begin{APACrefauthors}%
Gosselin, R\BHBI D.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2020}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Statistical Analysis Must Improve to Address the
  Reproducibility Crisis: The ACcess to Transparent Statistics (ACTS) Call to
  Action} {Statistical analysis must improve to address the reproducibility
  crisis: The access to transparent statistics (acts) call to action}.{\BBCQ}
\newblock
\APACjournalVolNumPages{BioEssays}{42}{1}{1900189}.
\newblock
\begin{APACrefURL}
  \url{https://onlinelibrary.wiley.com/doi/abs/10.1002/bies.201900189}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} 10.1002/bies.201900189 \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Henry%
\ \BBA {} Wickham%
}{%
Henry%
\ \BBA {} Wickham%
}{%
{\protect \APACyear {2020}}%
}]{%
R-tidyselect}
\APACinsertmetastar {%
R-tidyselect}%
\begin{APACrefauthors}%
Henry, L.%
\BCBT {}\ \BBA {} Wickham, H.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2020}{}{}.
\newblock
\APACrefbtitle {tidyselect: Select from a Set of Strings.} {tidyselect: Select
  from a set of strings.}
\newblock
\begin{APACrefURL} \url{https://CRAN.R-project.org/package=tidyselect}
  \end{APACrefURL}
\newblock
\APACrefnote{R package version 1.1.0}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Hermans%
\ \BBA {} Aldewereld%
}{%
Hermans%
\ \BBA {} Aldewereld%
}{%
{\protect \APACyear {2017}}%
}]{%
hermans2017programming}
\APACinsertmetastar {%
hermans2017programming}%
\begin{APACrefauthors}%
Hermans, F.%
\BCBT {}\ \BBA {} Aldewereld, M.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2017}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Programming is writing is programming} {Programming is
  writing is programming}.{\BBCQ}
\newblock
\BIn{} \APACrefbtitle {Companion to the first International Conference on the
  Art, Science and Engineering of Programming} {Companion to the first
  international conference on the art, science and engineering of programming}\
  (\BPGS\ 1--8).
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Kitzes%
, Turek%
\BCBL {}\ \BBA {} Deniz%
}{%
Kitzes%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2017}}%
}]{%
kitzes2017practice}
\APACinsertmetastar {%
kitzes2017practice}%
\begin{APACrefauthors}%
Kitzes, J.%
, Turek, D.%
\BCBL {}\ \BBA {} Deniz, F.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYear{2017}.
\newblock
\APACrefbtitle {The Practice of Reproducible Research: Case Studies and Lessons
  from the Data-Intensive Sciences} {The practice of reproducible research:
  Case studies and lessons from the data-intensive sciences}.
\newblock
\APACaddressPublisher{Berkeley, CA}{University of California Press}.
\newblock
\begin{APACrefURL} \url{https://www.practicereproducibleresearch.org}
  \end{APACrefURL}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Martinez%
\ \protect \BOthers {.}}{%
Martinez%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2018}}%
}]{%
r-opensci}
\APACinsertmetastar {%
r-opensci}%
\begin{APACrefauthors}%
Martinez, C.%
, Hollister, J.%
, Marwick, B.%
, Sz{\"o}cs, E.%
, Zeitlin, S.%
, Kinoshita, B\BPBI P.%
\BDBL {}Meinke, B.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2018}{}{}.
\newblock
\APACrefbtitle {{Reproducibility in Science: A Guide to enhancing
  reproducibility in scientific results and writing}.} {{Reproducibility in
  Science: A Guide to enhancing reproducibility in scientific results and
  writing}.}
\newblock
\begin{APACrefURL} \url{http://ropensci.github.io/reproducibility-guide/}
  \end{APACrefURL}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Marwick%
}{%
Marwick%
}{%
{\protect \APACyear {2019}}%
}]{%
R-rrtools}
\APACinsertmetastar {%
R-rrtools}%
\begin{APACrefauthors}%
Marwick, B.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2019}{}{}.
\newblock
\APACrefbtitle {rrtools: Creates a Reproducible Research Compendium.} {rrtools:
  Creates a reproducible research compendium.}
\newblock
\begin{APACrefURL} \url{https://github.com/benmarwick/rrtools} \end{APACrefURL}
\newblock
\APACrefnote{R package version 0.1.0}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Marwick%
, Boettiger%
\BCBL {}\ \BBA {} Mullen%
}{%
Marwick%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2018}}%
}]{%
marwick2018packaging}
\APACinsertmetastar {%
marwick2018packaging}%
\begin{APACrefauthors}%
Marwick, B.%
, Boettiger, C.%
\BCBL {}\ \BBA {} Mullen, L.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2018}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Packaging data analytical work reproducibly using {R}
  (and friends)} {Packaging data analytical work reproducibly using {R} (and
  friends)}.{\BBCQ}
\newblock
\APACjournalVolNumPages{The American Statistician}{72}{1}{80--88}.
\newblock
\begin{APACrefURL} \url{https://peerj.com/preprints/3192.pdf} \end{APACrefURL}
\newblock
\begin{APACrefDOI} doi.org/10.1080/00031305.2017.1375986 \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
McArthur%
}{%
McArthur%
}{%
{\protect \APACyear {2019}}%
}]{%
engineering-reproducibility}
\APACinsertmetastar {%
engineering-reproducibility}%
\begin{APACrefauthors}%
McArthur, S\BPBI L.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2019}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Repeatability, Reproducibility, and Replicability:
  Tackling the 3R challenge in biointerface science and engineering}
  {Repeatability, reproducibility, and replicability: Tackling the 3r challenge
  in biointerface science and engineering}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Biointerphases}{14}{2}{1--2}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1116/1.5093621} \end{APACrefURL}
\newblock
\begin{APACrefDOI} 10.1116/1.5093621 \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
McIntire%
\ \BBA {} Chubaty%
}{%
McIntire%
\ \BBA {} Chubaty%
}{%
{\protect \APACyear {2020}}%
}]{%
R-reproducible}
\APACinsertmetastar {%
R-reproducible}%
\begin{APACrefauthors}%
McIntire, E\BPBI J\BPBI B.%
\BCBT {}\ \BBA {} Chubaty, A\BPBI M.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2020}{}{}.
\newblock
\APACrefbtitle {reproducible: A Set of Tools that Enhance Reproducibility
  Beyond Package Management.} {reproducible: A set of tools that enhance
  reproducibility beyond package management.}
\newblock
\begin{APACrefURL} \url{https://CRAN.R-project.org/package=reproducible}
  \end{APACrefURL}
\newblock
\APACrefnote{R package version 1.0.0}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
OpenSci%
}{%
OpenSci%
}{%
{\protect \APACyear {2020}}%
}]{%
R-drake}
\APACinsertmetastar {%
R-drake}%
\begin{APACrefauthors}%
OpenSci, R.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2020}{}{}.
\newblock
\APACrefbtitle {drake: A Pipeline Toolkit for Reproducible Computation at
  Scale.} {drake: A pipeline toolkit for reproducible computation at scale.}
\newblock
\begin{APACrefURL} \url{https://cran.r-project.org/package=drake}
  \end{APACrefURL}
\newblock
\APACrefnote{R package version 7.11.0}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
{Oracle Corporation}%
}{%
{Oracle Corporation}%
}{%
{\protect \APACyear {2019}}%
}]{%
wercker}
\APACinsertmetastar {%
wercker}%
\begin{APACrefauthors}%
{Oracle Corporation}.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2019}{}{}.
\newblock
\APACrefbtitle {Wercker.} {Wercker.}
\newblock
\begin{APACrefURL} \url{https://github.com/wercker/wercker} \end{APACrefURL}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Patil%
, Peng%
\BCBL {}\ \BBA {} Leek%
}{%
Patil%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2019}}%
}]{%
patil2019visual}
\APACinsertmetastar {%
patil2019visual}%
\begin{APACrefauthors}%
Patil, P.%
, Peng, R\BPBI D.%
\BCBL {}\ \BBA {} Leek, J\BPBI T.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2019}{}{}.
\newblock
{\BBOQ}\APACrefatitle {A visual tool for defining reproducibility and
  replicability} {A visual tool for defining reproducibility and
  replicability}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Nature human behaviour}{3}{7}{650--652}.
\newblock
\begin{APACrefURL} \url{https://www.nature.com/articles/s41562-019-0629-z}
  \end{APACrefURL}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Peng%
}{%
Peng%
}{%
{\protect \APACyear {2009}}%
}]{%
peng2009bio}
\APACinsertmetastar {%
peng2009bio}%
\begin{APACrefauthors}%
Peng, R\BPBI D.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2009}{07}{}.
\newblock
{\BBOQ}\APACrefatitle {{Reproducible research and Biostatistics}}
  {{Reproducible research and Biostatistics}}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Biostatistics}{10}{3}{405-408}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1093/biostatistics/kxp014}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} 10.1093/biostatistics/kxp014 \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}
